\input font_century
\input url

\frenchspacing
\footline{\tenrm\fontspacing Phone: 530--262--4702\hfill Email: \url{robert\_crummett@mines.edu}}

% https://ctan.org/pkg/font-change
\def\fontspacing{\baselineskip=2.8ex plus0pt minus0pt\spaceskip=0.333333em plus0.122222em minus0.0999999em}

\twentyrm
\fontspacing
\noindent
Philosophy\kern5pt of\kern7pt Teaching
\bigskip

\tenrm
\fontspacing
\noindent
The best course I ever took was taught by Dr.~Greg~Fausshauer, {\it Kernel-based Approximation Methods}.
Dr.~Fausshauer is both a talented researcher and communicator.
But what set his course apart was his altruistic approach to teaching.
He would take long, preplanned tangents mid-lecture to form connections between our personal research interests and the day's lecture material.
He encouraged pre lecture research discussions, many of which were extended into his lecture time.
Discussion was so rich, I would show up 15 minutes before class just to make sure I missed none of it.
By the end of the semester, Dr.~Fausshauer was closer to a second advisor than a professor.

\medskip
\noindent
I seek to emulate much of Dr.~Fausshauer's instructional style in my own classroom.
As a teacher's assistant, I have had the opportunity to create assignments for students to work on.
I seek to give students the creative freedom to integrate their own research interests into the assignments by providing what I call {\it flexible prompts}.
Flexible prompts permit the student to integrate their personal interests with the learning goals of the course.

\bye
