\input font_century
\input enumerate
\input url

\frenchspacing
\footline{\tenrm\fontspacing Phone: 530--262--4702\hfill Email: \url{robert\_crummett@mines.edu}}

% https://ctan.org/pkg/font-change
\def\fontspacing{\baselineskip=2.8ex plus0pt minus0pt\spaceskip=0.333333em plus0.122222em minus0.0999999em}

\twentyrm
\fontspacing
\noindent
Robert~Nate~Crummett

\kern2pt
\hrule height 1pt
\smallskip

\eightrm
\fontspacing
\line{Geophysics PhD student at the Colorado~School~of~Mines focused on accelerating regional-scale mineral exploration techniques}
\bigskip

\setbox0=\hbox{\sixteenrm\fontspacing Experience}
{\copy0}
\kern-1.5pt
\hrule width \wd0 height 0.8pt
\medskip

\noindent
{\twelverm\fontspacing PhD Student advised by Dr.~Yaoguo~Li}
\hfill{\eightit\fontspacing August 2023--Present}
\tenrm
\fontspacing

\kern-4pt
\beginenumerate
\item Research Assistant in the Center for Gravity, Electric and Magnetic Studies (CGEM) at the Colorado School of Mines.
Researching methods to accelerate regional exploration.
The first chapter of my thesis is focused on improving the reduction to the pole.
\item Daily work includes coding, writing, reading, and presenting science in a classroom setting.
\item Presented posters and talks about mineral exploration geophysics at IMAGE 2024 and AME 2025.
\endenumerate

\noindent
{\twelverm\fontspacing Field Tech with Zonge International}
\hfill{\eightit\fontspacing May 2022--August 2023}

\kern-4pt
\beginenumerate
\item Flew over 1000 km of billable drone magnetic surveys on contracts, primarily for mineral exploration.
I am familiar with state of the art collection of drone magnetic data and technologies.
\item Spearheaded UAV safety program.
I compiled the FAA's requirements for commercial UAV programs and synthesized them into a first-draft safety action plan and program complying with United States regulations.
Today, this safety program is the best in the world of exploration.
\item Led and participated in spectral IP, gravity, CSAMT, and MT surveys.
A variety of manual labor, coordination (4--12 people per survey), taking notes, repairing mechanical equipment, and basic data processing.
\endenumerate

\noindent
{\twelverm\fontspacing Research Scientist with University of Nevada-Reno}
\hfill{\eightit\fontspacing May 2022--August 2023}

\kern-4pt
\beginenumerate
\item Modelled influence of glacial loads on hydrothermal system activity.
\item Presented the work as a poster at AGU 2022.
\endenumerate
\medskip

\setbox0=\hbox{\sixteenrm\fontspacing Education}
{\copy0}
\kern1.5pt
\hrule width \wd0 height 0.8pt
\medskip

\noindent
{\twelverm\fontspacing PhD in Geophysics --- Colorado School of Mines}
\hfill{\eightit\fontspacing August 2023--Present}

\kern2pt
\noindent
\line{Advised by Dr.~Yaoguo~Li\hfil Minor in Mathematics\hfil Degree In Progress}
\medskip

\noindent
{\twelverm\fontspacing Bachelor of Science in Geophysics --- University of Nevada-Reno}
\hfill{\eightit\fontspacing August 2020--May 2022}
\medskip

\setbox0=\hbox{\sixteenrm\fontspacing Skills}
{\copy0}
\kern1.5pt
\hrule width \wd0 height 0.8pt

\beginenumerate
\item Magnetic Geophysics --- Theoretical knowledge and practical know-how.
\item Computers --- Programming in a dozen languages.
Comfortable in Windows, Linux and MacOS.
\item Drones --- Licensed FAA Pilot.
Over 1000 km of commercial mineral exploration surveys.
\item Communication --- Presented at various professional conferences on exploration geophysics.
\endenumerate
\smallskip

\setbox0=\hbox{\sixteenrm\fontspacing Publications and Presentations}
{\copy0}
\kern1.5pt
\hrule width \wd0 height 0.8pt

\beginenumerate
\item Crummett,~R.~N.~\&~Li,~Y., Low Latitude Reduction to Pole in Regional Mineral Exploration:  4th International Meeting for Applied Geoscience \& Energy, IMAGE. Short Abstract.
\smallskip
\item Crummett,~R.~N.,~Zhang,~M.,~\&~Li,~Y., Reformulation of the Reduction to the Pole by Reduction to the Equator Operators: Association for Mineral Exploration (AME) Roundup, 2025. Poster.
\endenumerate
\smallskip

\setbox0=\hbox{\sixteenrm\fontspacing Links}
{\copy0}
\kern1.5pt
\hrule width \wd0 height 0.8pt
\medskip

\noindent
{\ninebf CGEM:}\quad \url{https:/cgem.mines.edu}

\noindent
{\ninebf Zonge:}\quad \url{http:/zonge.com}

\noindent
{\ninebf Github:}\quad \url{https:/github.com/RobertCrummett}

\noindent
{\ninebf LinkedIn:}\quad \url{https:/linkedin.com/in/robert-crummett}
\bye
